\onehalfspacing
\addcontentsline{toc}{chapter}{Acknowledgements}
%\setlength{\beforechapskip}{20pt}
\chapter*{Acknowledgements}
%\addcontentsline{toc}{chapter}{\protect\numberline{}Acknowledgement}
\setlength{\parindent}{0pt} 
\setlength{\parskip}{1ex}

First and foremost, I extend my profound gratitude to my advisor, Professor Chetan Arora, who has not only been a brilliant mentor but also the source of motivation throughout my journey. His unwavering support has always been a constant by my side, guiding me through both academic challenges and life's uncertainties. I deeply value his brilliant research advice and insightful discussions, without which this work would not have been achievable. I owe a debt of gratitude to him for believing in me during the initial tumultuous days of my PhD.

I am indebted to Dr. Pankaj Gupta from PGIMER, Chandigarh, who has been a truly motivating clinician-cum-academic. His consistent efforts, collaboration, and enriching discussions on clinical aspects have played a pivotal role in shaping and realizing the work. I am also thankful to my SRC members, Prof. Prem Kalra, Prof. Parag Singla, and Prof. Rohan Paul for their insightful suggestions regarding improving the work. I am also thankful to CSE staff -- Ms. Rekha, Mr. Hemant, Mr. Vikash and the Department of CSE for their continual support throughout my journey. 

I extend heartfelt thanks to the bright and talented co-authors -- Mayank Gupta, Dr. Pratyaksha Rana, Somanshu Singla, Mayuna Gupta, Chetan Madan, and Ashish Papanai -- whose contributions have been instrumental. I also thank Nikhil, Ankita, Ramya, Anupam, Britty, Kunal, Ajay, Rohan, Prashant, and other vision group students for the enriching conversations from time to time. Additionally, I thank my friends, Vipul, Aritra, Argha, Arpan, Arkajyoti, Shivani, Sahil, Swaraj, Soham, Suvo, Avik, Arijit, Shamik, Biman, and many others for their support and cheerful company during the exhausting phases of this journey. 

I want to express my deepest gratitude to all of my teachers who have played a pivotal role in shaping my journey starting from kindergarten to school, through universities. Thank you for inspiring and supporting me, and making me who I am today.

I am profoundly grateful to my family, especially my wife, Arunima, my son, Syamantak, and my father, Mr. Jyotirmoy Basu, who have been the consistent pillars of support throughout this journey. They have been relentlessly there for me through thick and thin, and no amount of gratitude is enough. I am equally grateful to my mother-in-law, Mrs. Suparna Maitra, for her constant motivation. 

I am forever indebted to two dear ones watching me from their heavenly abode: my mother, Mrs. Leena Basu, and my father-in-law, Dr. Ashok Maitra. Without their dream, motivation, and support, I would not have stepped into the journey of a PhD.  Finally, I humbly bow down to the supreme lord for showering all the love and blessings throughout all this time.

\vspace{2cm}
{ \begin{flushright}{\bf Soumen Basu}\end{flushright} }
