\addcontentsline{toc}{chapter}{List of Publications}

\chapter*{List of Publications}
\section*{Part of this Thesis}
\subsection*{Journal}
\begin{enumerate}[label={[J.\arabic*]}]
    \item Soumen Basu, Mayank Gupta, Pratyaksha Rana, Pankaj Gupta, and Chetan Arora. ``RadFormer: Transformers with global–local attention for interpretable and accurate Gallbladder Cancer detection.'' Medical Image Analysis 83 (2023): 102676.
\end{enumerate}

\subsection*{Conference}
\begin{enumerate}[label={[C.\arabic*]}]
    \item \textbf{Soumen Basu}, Mayank Gupta, Pratyaksha Rana, Pankaj Gupta, and Chetan Arora. ``Surpassing the human accuracy: detecting gallbladder cancer from USG images with curriculum learning.'' In Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR), pp. 20886-20896, 2022.
    \item \textbf{Soumen Basu}, Somanshu Singla, Mayank Gupta, Pratyaksha Rana, Pankaj Gupta, and Chetan Arora. ``Unsupervised Contrastive Learning of Image Representations from Ultrasound Videos with Hard Negative Mining.'' In International Conference on Medical Image Computing and Computer-Assisted Intervention (MICCAI), pp. 423-433, 2022.
    \item \textbf{Soumen Basu}, Ashish Papanai, Mayank Gupta, Pankaj Gupta, and Chetan Arora. ``Gall Bladder Cancer Detection from US Images with only Image Level Labels.'' In International Conference on Medical Image Computing and Computer-Assisted Intervention (MICCAI), pp. 206-215, 2023.
%\end{enumerate}
%\subsection*{Under Communication}
%\begin{enumerate}[label={[U.\arabic*]}]
    \item \textbf{Soumen Basu}, Mayuna Gupta, Chetan Madan, Pankaj Gupta, and Chetan Arora. ``FocusMAE: Gallbladder Cancer Detection from Ultrasound Videos with Focused Masked Autoencoders.'' IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR), pp. 11715-11725, 2024.
\end{enumerate}

\section*{Not a part of this Thesis}
\subsection*{Journal}
\begin{enumerate}[label={[J.\arabic*]}]
\setcounter{enumi}{1}
    \item Pankaj Gupta, Soumen Basu et al. "Deep-learning enabled ultrasound based detection of gallbladder cancer in northern India: a prospective diagnostic study." The Lancet Regional Health-Southeast Asia (2023).
    \item Pankaj Gupta, Soumen Basu et al. "Deep-learning models for differentiation of xanthogranulomatous cholecystitis and gallbladder cancer on ultrasound." Indian Journal of Gastroenterology (2023): 1-8.
\end{enumerate}
\subsection*{Conference}
\begin{enumerate}[label={[C.\arabic*]}]
\setcounter{enumi}{3}
    \item Mayank Gupta, Soumen Basu, and Chetan Arora. "How Reliable are the Metrics Used for Assessing Reliability in Medical Imaging?." In International Conference on Medical Image Computing and Computer-Assisted Intervention (MICCAI), pp. 149-158, 2023.
\end{enumerate}
