\chapter{Video-based Detection of GBC}
%
\label{chap:focusmae}
%
%\input{chapters/focusmae/sections/abstract}

In the previous chapters, we have developed comprehensive methods for detecting Gallbladder Cancer (GBC) from Ultrasound (USG) images. However, these methodologies lack the advantage of the rich spatiotemporal information available in the full USG videos. Individual USG images may lack sufficient information to capture the disease manifestation. In this chapter, we advocate for a paradigm shift towards video-based GBC detection, leveraging the inherent advantages of spatiotemporal representations. Video-based detection also helps to streamline the detection process and mitigate the effect of operator-specific variations by omitting the need of specific key frame selection by human radiologists. We use a Masked Autoencoder (MAE) framework for self-supervised pretraining of the videos-based GBC detection models. The self-supervised pre-training is followed by the downstream video-based GBC detection task.
%While video-based GBC classification demonstrates improvements, a meticulous examination reveals an opportunity for refinement to the random masking intrinsic to MAE. 
We propose a novel design called \focusmae to systematically bias the selection of masking tokens from high-information regions, fostering a more refined representation of malignancy. %Additionally, we contribute the most extensive US video dataset for GBC detection. We also note that, this is the first study on US video-based GBC detection. 
%We validate the proposed methods on the curated dataset, and report a new state-of-the-art (SOTA) accuracy of 96.4\% for the GBC detection problem, against an accuracy of 84\% by current SOTA - GBCNet, and RadFormer. We further demonstrate the generality of the proposed \focusmae on a public CT-based Covid detection dataset, reporting an improvement in accuracy by 2.2\% over current baselines.

This chapter is based on the following work:
\par \noindent [1] \textit{Soumen Basu, Mayuna Gupta, Chetan Madan, Pankaj Gupta, and Chetan Arora. ``FocusMAE: Gallbladder Cancer Detection from Ultrasound Videos with Focused Masked Autoencoders.'' IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR), 2024}.

\input{chapters/focusmae/sections/introduction}

\input{chapters/focusmae/sections/rel_work}

\input{chapters/focusmae/sections/method}

\input{chapters/focusmae/sections/data}

\input{chapters/focusmae/sections/implementation}

\input{chapters/focusmae/sections/table-main}

\input{chapters/focusmae/sections/result}

\input{chapters/focusmae/sections/conclusion}
