
%\begin{abstract}
We explore the potential of \cnn-based models for gallbladder cancer (\gbc) detection from ultrasound (\usg) images as no prior study is known. \usg is the most common diagnostic modality for \gb diseases due to its low cost and accessibility. However, \usg images are challenging to analyze due to low image quality, noise, and varying viewpoints due to the handheld nature of the sensor. Our exhaustive study of state-of-the-art (\sota) image classification techniques for the problem reveals that they often fail to learn the salient \gb region due to the presence of shadows in the \usg images. \sota object detection techniques also achieve low accuracy because of spurious textures due to noise or adjacent organs. We propose GBCNet to tackle the challenges in our problem. GBCNet first extracts the regions of interest (\rois) by detecting the \gb (and not the cancer), and then uses a new multi-scale, second-order pooling architecture specializing in classifying \gbc. To effectively handle spurious textures, we propose a curriculum inspired by human visual acuity, which reduces the texture biases in GBCNet. Experimental results demonstrate that GBCNet significantly outperforms \sota \cnn models, as well as the expert radiologists. Our technical innovations are generic to other \usg image analysis tasks as well. Hence, as a validation, we also show the efficacy of GBCNet in detecting  breast cancer from \usg images. Project page with source code, trained models, and data is available at \href{https://gbc-iitd.github.io/gbcnet.html}{\texttt{https://gbc-iitd.github.io/gbcnet}}. %\footnote{\href{https://github.com/sbasu276/GBCNet}{https://github.com/sbasu276/GBCNet}}.
%\footnote{\href{https://anonymous.4open.science/r/GBCNet}{https://anonymous.4open.science/r/GBCNet}}.
%\end{abstract}

% \begin{abstract}
% We explore the potential of \cnn based models for gallbladder cancer (\gbc) detection from ultrasound sonography (\usg) images as no prior study is known. \usg is the most common diagnostic modality for \gbc detection due to its low cost and accessibility. However, \usg images are challenging to analyze due to low image quality, noise, and varying viewpoints due to the handheld nature of the sensor. Our exhaustive study of state-of-the-art (\sota) image classification techniques for the problem reveals that they often fail to learn the salient \gb region due to the presence of shadows in the \usg images. \sota object detection techniques also achieve low accuracy because of spurious textures due to noise or adjacent organ tissues. Realizing the challenges in our problem, we propose a three-stage neural network architecture for \gbc detection. The first two stages are inspired from the two-stage object detectors but focus only on detecting the \gb (and not the \gbc). The third stage uses a new multi-scale, second-order pooling architecture and specializes in classifying gallbladder malignancy. To effectively handle spurious textures, we propose a curriculum inspired by human visual acuity, which reduces the texture biases in GBCNet. Experimental results demonstrate that GBCNet significantly outperforms \sota \cnn models, as well as even the expert radiologists. Many of our technical innovations are generic to \usg image analysis. Hence, as a validation, we also show the efficacy of GBCNet in detecting malignancy on a breast cancer \usg dataset. We are releasing our source code and pre-trained models\footnote{\href{https://anonymous.4open.science/r/GBCNet}{https://anonymous.4open.science/r/GBCNet}}.
% \end{abstract}
